MS_CNuptake.Rmd

### 2022-07-12 MS_CNuptake.Rmd

# Setup 
```{r setup, include=FALSE}
rm(list=ls())
library(MLmetrics)
library(vhs)
library(tidyverse) 
library(ncmeta)
library(viridis)
library(ggthemes)
library(LSD)
library(yardstick)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(gplots)
library(tidyselect)
library(extrafont)
library(caret)
library(recipes)
#remotes::install_github("cj-holmes/vhs")
#devtools::load_all("/Users/yunpeng/yunkepeng/rbeni_new/rbeni/") # using beni's latest package.
library(rbeni)
library(raster)
library(maps)
library(rworldmap)
library(cowplot)
library(ncdf4)
library(scales)
library(lme4)
library(lmerTest)
library("PerformanceAnalytics")
library(MuMIn)
library(tidyverse)
library(ggplot2)
library(lme4)
library(visreg)
library(ggpubr)
library(car)
library("ggplotify")
library(remotes)
library(tune)
library(relaimpo)

@@

### BP vs. model predictors
```{r}
#now, start works
BP_dataset2 <- na.omit(NPP_forest[,c("tnpp_a","age_a","fAPAR_a","CNrt_a","Tg_a","PPFD_a","vpd_a","site_a")])
dim(BP_dataset2)
a2 <- stepwise(BP_dataset2,"tnpp_a")
a2[[1]]
a2[[2]]
a2[[3]]
bp_model <- (lmer(tnpp_a~Tg_a+fAPAR_a+PPFD_a+CNrt_a+age_a+(1|site_a),data=BP_dataset2))
summary(bp_model)
r.squaredGLMM(bp_model)

@@

### ANPP vs. modelled predictors
```{r}
anpp_tnpp_dataset2 <- na.omit(NPP_forest[,c("anpp_tnpp_a","age_a","fAPAR_a","CNrt_a","Tg_a","PPFD_a","vpd_a","site_a")])
dim(subset(NPP_forest,ANPP_2>0))
model2a <- stepwise(anpp_tnpp_dataset2,"anpp_tnpp_a")
model2a[[1]]
model2a[[2]]
model2a[[3]]
anpp_tnpp_model <- (lmer(anpp_tnpp_a~CNrt_a+PPFD_a+Tg_a+age_a+(1|site_a),data=anpp_tnpp_dataset2))
summary(anpp_tnpp_model)
r.squaredGLMM(anpp_tnpp_model)

@@

## NRE 
```{r}
#NRE = 69%
NRE_Du <- read.csv(file="~/data/NRE_various/NRE_Du/NRE_Du.csv")
NRE_Dong <- read.csv(file="~/data/NRE_various/NRE_Deng/NRE_Deng.csv")

@@

plot_grid(aa1,aa2,aa3,aa4,aa5,aa6,aa7,aa8,
          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)'),label_size = 15)+white
ggsave(paste("./output/newphy_figs7.jpg",sep=""),width = 22, height = 10)
```

### Global maps of each predictors
```{r warning=FALSE}
#figs2 representing all predictors
gg <- plot_map3(na.omit(CNrt[,c("lon","lat","CNrt")]),varnam = "CNrt",latmin = -65, latmax = 85,combine=FALSE)
d1 <- gg$ggmap +labs(title = "Soil C/N")+theme_grey(base_size = 15)+ white;d2 <- gg$gglegend+ white

@@

ISAM_fNup <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/ISAM_S2_fNup_ANN_mean.nc"), varnam = "fNup"))
ISAM_fNup$fNup<- ISAM_fNup$fNup*1000*31556952

ISAM_gpp <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/ISAM_S2_gpp_ANN_mean.nc"), varnam = "gpp"))
ISAM_gpp$gpp<- ISAM_gpp$gpp*1000*31556952

ISAM_npp <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/ISAM_S2_npp_ANN_mean.nc"), varnam = "npp"))
ISAM_npp$npp<- ISAM_npp$npp*1000*31556952

@@

## TRENDY analysis- BP
```{r, warning=FALSE}

#all_maps
not_used <- list(CLASS_GPP,CLASS_NPP,CLM_GPP,CLM_NPP,JSBACH_fNup,JSBACH_GPP,JSBACH_NPP)

@@

## Plot partial dependencies
```{r, warning=FALSE}

@@

## TRENDY analysis - N uptake
```{r, warning=FALSE}

#nuptake figure
#N minerlization
Nmin_statistical <- subset(NPP_forest,Nmin>0)

@@

## TRENDY analysis - NUE
```{r, warning=FALSE}

#nue model for TRENDY
#nuptake figure
#N minerlization
NUE_test <- NPP_all

@@

@@

ggsave(paste("./output/newphy_fortable2.jpg",sep=""), width = 23, height = 25)

## N uptake validation between models
```{r, warning=FALSE}
#validation - N uptake
Nmin_statistical$pred_nuptake

@@

## visreg for BP and anpp/bp vs. all measured predictors
```{r}
#visreg

@@

### statistics of uncertainty
```{r}
#all statistics
#forest
sum(uncertainty_npp*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_anpp*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_bnpp*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_lnpp*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_wnpp*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_lnf*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_wnf*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_bnf*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_nuptake*(forest_percent *conversion)*available_grid2,na.rm=TRUE)

@@

### BP partial relationship vs. observations
```{r}
#partial residual figure
BP_dataset <- na.omit(NPP_forest[,c("tnpp_a","obs_age_a","observedfAPAR_a","soilCN_a","Tg_a","PPFD_a","vpd_a","site_a")])
#model1 <- stepwise(BP_dataset,"tnpp_a")
#model1[[1]]
#model1[[2]]
bp_model <- (lmer(tnpp_a~Tg_a+PPFD_a+soilCN_a+obs_age_a+observedfAPAR_a+(1|site_a),data=BP_dataset))
summary(bp_model)

>>>>

# Setup 
```{r setup, include=FALSE}
library(MLmetrics)
library(vhs) # remotes::install_github("cj-holmes/vhs")
library(tidyverse) 
library(ncmeta)
library(viridis)
library(ggthemes)
library(LSD)
library(yardstick)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(gplots)
library(tidyselect)
library(extrafont)
library(caret)
library(recipes)
#devtools::load_all("/Users/yunpeng/yunkepeng/rbeni_new/rbeni/") # using beni's latest package.
library(rbeni)
library(raster)
library(maps)
library(rworldmap)
library(cowplot)
library(ncdf4)
library(scales)
library(lme4)
library(lmerTest)
library("PerformanceAnalytics")
library(MuMIn)
library(tidyverse)
library(ggplot2)
library(lme4)
library(visreg)
library(ggpubr)
library(car)
library("ggplotify")
library(remotes)
library(tune)
library(relaimpo)

@@

### BP vs. model predictors

```{r}
#now, start works
BP_dataset2 <- na.omit(NPP_forest[,c("tnpp_a","age_a","fAPAR_a","CNrt_a","Tg_a","PPFD_a","vpd_a","site_a")])
dim(BP_dataset2)
a2 <- stepwise(BP_dataset2,"tnpp_a")
a2[[1]]
a2[[2]]
a2[[3]]
bp_model <- (lmer(tnpp_a~Tg_a+fAPAR_a+PPFD_a+CNrt_a+age_a+(1|site_a),data=BP_dataset2))
summary(bp_model)
r.squaredGLMM(bp_model)

@@

### ANPP vs. modelled predictors

```{r}
anpp_tnpp_dataset2 <- na.omit(NPP_forest[,c("anpp_tnpp_a","age_a","fAPAR_a","CNrt_a","Tg_a","PPFD_a","vpd_a","site_a")])
dim(subset(NPP_forest,ANPP_2>0))
model2a <- stepwise(anpp_tnpp_dataset2,"anpp_tnpp_a")
model2a[[1]]
model2a[[2]]
model2a[[3]]
anpp_tnpp_model <- (lmer(anpp_tnpp_a~CNrt_a+PPFD_a+Tg_a+age_a+(1|site_a),data=anpp_tnpp_dataset2))
summary(anpp_tnpp_model)
r.squaredGLMM(anpp_tnpp_model)

@@

## NRE

```{r}
#NRE = 69%
NRE_Du <- read.csv(file="~/data/NRE_various/NRE_Du/NRE_Du.csv")
NRE_Dong <- read.csv(file="~/data/NRE_various/NRE_Deng/NRE_Deng.csv")

@@

#plot_grid(aa1,aa2,aa3,aa4,aa5,aa6,aa7,aa8,
#          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)'),label_size = 15)+white
#ggsave(paste("~/data/output/newphy_fig4_parallel.jpg",sep=""),width = 22, height = 10)
```

### Global maps for effect of each factor NUE (not used now)

```{r}
gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_CNrt")]),varnam = "nue_CNrt",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4", "wheat","tomato3"),
                breaks = seq(-0.05,0.05,0.01))
g1 <- gg$ggmap +labs(title = "Soil C/N")+theme_grey(base_size = 15);g2 <- gg$gglegend

gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_age")]),varnam = "nue_age",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4","royalblue3","wheat","tomato3"),
                breaks = seq(-0.05,0.05,0.01))
g3 <- gg$ggmap +labs(title = "Age")+theme_grey(base_size = 15);g4 <- gg$gglegend+labs(title = ~paste("years"))

gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_fAPAR")]),varnam = "nue_fAPAR",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4","royalblue3", "wheat","tomato3"),
                breaks = seq(-0.04,0.04,0.01))
g5 <- gg$ggmap +labs(title = "fAPAR")+theme_grey(base_size = 15);g6 <- gg$gglegend

gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_PPFD")]),varnam = "nue_PPFD",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4", "wheat","tomato3","tomato4"),
                breaks = seq(-0.08,0.12,0.02))
g7 <- gg$ggmap +labs(title = "PPFD")+theme_grey(base_size = 15);g8 <- gg$gglegend + labs(title =~paste(mu, "mol m"^-2,"s"^-1))

gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_Tg")]),varnam = "nue_Tg",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4", "wheat","tomato3"),
                breaks = seq(-0.30,0.30,0.10))
g9 <- gg$ggmap +labs(title =~paste(T[g]))+theme_grey(base_size = 15);g10 <- gg$gglegend + labs(title =~paste("\u00B0C"))

gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_vpd")]),varnam = "nue_vpd",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4", "wheat","tomato3"),
                breaks = seq(-0.20,0.30,0.05))
g11 <- gg$ggmap +labs(title = "D")+theme_grey(base_size = 15);g12 <- gg$gglegend+ labs(title =~paste("kPa"))

gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_vcmax25")]), varnam = "nue_vcmax25",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4", "wheat","tomato3"),
                breaks = seq(-0.2,0.2,0.04))
g15 <- gg$ggmap +labs(title =~paste(V[cmax25]))+theme_grey(base_size = 15);g16 <- gg$gglegend+ labs(title =~paste(mu, "mol m"^-2,"s"^-1))

gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_LMA")]),varnam = "nue_LMA",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4", "wheat","tomato3"),
                breaks = seq(-0.05,0.05,0.01))
g17 <- gg$ggmap +labs(title = "LMA")+theme_grey(base_size = 15);g18 <- gg$gglegend+ labs(title =~paste("g ","m"^-2))

#plot_grid(g1,g2,g3,g4,g5,g6,
#          g7,g8,g9,g10,g11,g12,
#          g15,g16,g17,g18,
#          nrow=3,rel_widths = c(3/12, 1/12,3/12,1/12,3/12,1/12),
#          labels = c('(a)',' ','(b)',' ','(c)',' ',
#                     '(d)',' ','(e)',' ','(f)',' ',
#                     '(g)',' ','(h)',' '),label_size = 15)+white
#
#ggsave(paste("~/data/output/newphy_fig4_not_used.jpg",sep=""),width = 20, height = 10)

g1
g2
g3
g4
g5
g6
g7
g8
g9
g10
g11
g12
g15
g16
g17
g18
=======
plot_grid(aa1,aa2,aa3,aa4,aa5,aa6,aa7,aa8,
          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)'),label_size = 15)+white
ggsave(paste("./output/newphy_figs7.jpg",sep=""),width = 22, height = 10)
>>>>>>> dc4d6d3784f86766727dcb656a91a51ca08a6e24
```

### Global maps of each predictors

```{r warning=FALSE}
#figs2 representing all predictors
gg <- plot_map3(na.omit(CNrt[,c("lon","lat","CNrt")]),varnam = "CNrt",latmin = -65, latmax = 85,combine=FALSE)
d1 <- gg$ggmap +labs(title = "Soil C/N")+theme_grey(base_size = 15)+ white;d2 <- gg$gglegend+ white

@@

ISAM_fNup <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/ISAM_S2_fNup_ANN_mean.nc"), varnam = "fNup"))

# XXX what are these numbers that you multiply here?
ISAM_fNup$myvar<- ISAM_fNup$fNup*1000*31556952

ISAM_gpp <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/ISAM_S2_gpp_ANN_mean.nc"), varnam = "gpp"))
ISAM_gpp$myvar<- ISAM_gpp$gpp*1000*31556952

ISAM_npp <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/ISAM_S2_npp_ANN_mean.nc"), varnam = "npp"))
ISAM_npp$myvar<- ISAM_npp$npp*1000*31556952

@@

## BP

```{r}
#all_maps
not_used <- list(CLASS_GPP,CLASS_NPP,CLM_GPP,CLM_NPP,JSBACH_fNup,JSBACH_GPP,JSBACH_NPP)

@@

### Plot partial dependencies
```{r, warning=FALSE}

@@

## TRENDY analysis - N uptake
```{r, warning=FALSE}
#nuptake figure
#N minerlization
Nmin_statistical <- subset(NPP_forest,Nmin>0)

@@

### NUE

```{r, warning=FALSE}
#nue model for TRENDY
#nuptake figure
#N minerlization
NUE_test <- NPP_all

@@

## Nuptake or NUE vs. all predictors

```{r}
# n uptake
mod_nue3 <- (lm(pred_nuptake~LMA_a+fAPAR_a+age_a+vpd_a+CNrt_a+Tg_a+vcmax25_a+PPFD_a,data=nue_allplots))
summary(mod_nue3)
nue1c <- visreg(mod_nue3,"LMA_a",type="contrast")
nue2c <- visreg(mod_nue3,"fAPAR_a",type="contrast")
nue3c <- visreg(mod_nue3,"age_a",type="contrast")
nue4c <- visreg(mod_nue3,"vpd_a",type="contrast")
nue5c <- visreg(mod_nue3,"CNrt_a",type="contrast")
nue6c <- visreg(mod_nue3,"Tg_a",type="contrast")
nue7c <- visreg(mod_nue3,"vcmax25_a",type="contrast")
nue8c <- visreg(mod_nue3,"PPFD_a",type="contrast")

final1_nue1 <- ggplot() +geom_line(data = nue1c$fit, aes(LMA_a, visregFit),size=2) +ylab("N uptake") +  xlab("ln LMA") +theme_classic()+theme(text = element_text(size=20),legend.position="none")
final1_nue2 <- ggplot() +geom_line(data = nue2c$fit, aes(fAPAR_a, visregFit),size=2) + xlab("fAPAR") + ylab(" ")+theme_classic()+theme(text = element_text(size=20),legend.position="none")
final1_nue3 <- ggplot() +geom_line(data = nue3c$fit, aes(age_a, visregFit),size=2) + xlab("ln age") + ylab(" ")+theme_classic()+theme(text = element_text(size=20),legend.position="none")
final1_nue4 <- ggplot() +geom_line(data = nue4c$fit, aes(vpd_a, visregFit),size=2) + xlab("ln D") + ylab(" ")+theme_classic()+theme(text = element_text(size=20),legend.position="none")
final1_nue5 <- ggplot() +geom_line(data = nue5c$fit, aes(CNrt_a, visregFit),size=2)+ylab("N uptake")  + xlab("ln soil C/N") +theme_classic()+theme(text = element_text(size=20),legend.position="none")
final1_nue6 <- ggplot() +geom_line(data = nue6c$fit, aes(Tg_a, visregFit),size=2) + xlab("Tg") + ylab(" ")+theme_classic()+theme(text = element_text(size=20),legend.position="none")
final1_nue7 <- ggplot() +geom_line(data = nue7c$fit, aes(vcmax25_a, visregFit),size=2) + xlab("ln vcmax25") + ylab(" ")+theme_classic()+theme(text = element_text(size=20),legend.position="none")
final1_nue8 <- ggplot() +geom_line(data = nue8c$fit, aes(PPFD_a, visregFit),size=2) + xlab("ln PPFD") + ylab(" ")+theme_classic()+theme(text = element_text(size=20),legend.position="none")

#plot_grid(final1_nue1,final1_nue2,final1_nue3,final1_nue4,
#          final1_nue5,final1_nue6,final1_nue7,final1_nue8,
#          nrow=2,label_x = 0.8, label_y = 0.8)+white
```

@@

ggsave(paste("./output/newphy_fortable2.jpg",sep=""), width = 23, height = 25)
```

## N uptake validation between models

```{r, warning=FALSE}
#validation - N uptake
Nmin_statistical$pred_nuptake

@@

### visreg for BP and anpp/bp vs. all measured predictors
```{r}
#visreg

@@

### statistics of uncertainty

```{r}
#all statistics
#forest
sum(uncertainty_npp*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_anpp*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_bnpp*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_lnpp*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_wnpp*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_lnf*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_wnf*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_bnf*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_nuptake*(forest_percent *conversion)*available_grid2,na.rm=TRUE)

@@

### BP partial relationship vs. observations

```{r}
#partial residual figure
BP_dataset <- na.omit(NPP_forest[,c("tnpp_a","obs_age_a","observedfAPAR_a","soilCN_a","Tg_a","PPFD_a","vpd_a","site_a")])
#model1 <- stepwise(BP_dataset,"tnpp_a")
#model1[[1]]
#model1[[2]]
bp_model <- (lmer(tnpp_a~Tg_a+PPFD_a+soilCN_a+obs_age_a+observedfAPAR_a+(1|site_a),data=BP_dataset))
summary(bp_model)
